---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# **hdflex**

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center"
)
```


## About
This package contains the forecasting algorithm developed by [Ad채mmer, Lehmann and Sch체ssler (2023) ](https://www.researchgate.net/publication/367531209_Local_Predictability_in_High_Dimensions). Please cite the paper when using the package.

## Installation
You can install **hdflex** from [GitHub](https://github.com/lehmasve/hdflex):

``` r
# install.packages("devtools")
devtools::install_github("https://github.com/lehmasve/hdflex")
```

The package compiles some C++ source code for installation, which is why you need the appropriate compilers:
- On Windows you need [Rtools](https://cran.r-project.org/bin/windows/Rtools/) available from CRAN. 
- On macOS you need the very least Xcode and a Fortran compiler - for more details see (https://mac.r-project.org/tools/).

## Usage

```{r}
######### Forecast quarterly U.S. inflation ##########
### Please see Koop & Korobilis (2023) for further details regarding the dataset ###
# Packages
library("tidyverse")
library("hdflex")

# Set Target-Variables
target_var_names  <- c("GDPCTPI", "PCECTPI", "CPIAUCSL", "CPILFESL")

# Load Data
data  <-  inflation_data

# Loop over Target Variables
results <-  do.call("rbind", lapply(X = seq_along(target_var_names), FUN = function(p) { 

    # Y-Column-Name
    y_target    <-  paste(target_var_names[p], "h_1", sep = "_")
    y_signal    <-  target_var_names[p]
    not_target  <-  setdiff(paste(target_var_names, "h_1", sep = "_"), y_target)

    # Create Forecast-Dataset
    dataset  <-  data                                                                                     %>%
                  select(-any_of(c(y_signal, not_target)))                                                %>%
                  mutate(across(all_of(y_target), .fns = list("lag_1" = ~dplyr::lag(., 1))), .after = 2)  %>%
                  mutate(across(all_of(y_target), .fns = list("lag_2" = ~dplyr::lag(., 2))), .after = 3)  %>%
                  mutate(across(-c(1, 2, 3, 4), dplyr::lag))                                              %>%
                  slice(-c(1:3))                                                                          %>%
                  column_to_rownames("Date")                                                              %>%
                  as.matrix()
    
    # Get Dates & Length
    full_dates   <-  rownames(dataset)
    full_length  <-  length(full_dates)

    # Create Time-Sequence for loop
    T_full      <-  full_length -1
    T_sequence  <-  122:T_full 
    
    ### Benchmark Model ###
    # Create Result Matrices
    preds_ar2  <-  matrix(NA, ncol = 1, nrow = full_length, dimnames = list(full_dates, "AR"))
    se_ar2     <-  matrix(NA, ncol = 1, nrow = full_length, dimnames = list(full_dates, "AR"))
        
    # Loop over t
    for(t in T_sequence) {
            
        ### Pre-Process Data ###
        # Train Data
        x_train     <-  scale(dataset[1:t, -1, drop = FALSE])
        y_train     <-        dataset[1:t,  1, drop = FALSE]
  
        # Predict Data
        x_pred      <-  scale(dataset[1:(t+1), -1, drop = FALSE])[(t+1), , drop = FALSE]
        y_pred      <-        dataset[t+1, 1]

        ### Model 1: AR(2) ###
        # Train Data
        x_train_ar  <-  cbind(int = 1, x_train[, c(1:2), drop = FALSE])

        # Predict Data
        x_pred_ar   <-  cbind(int = 1,  x_pred[, c(1:2), drop = FALSE])

        # Fit Regressions
        model_ar    <-  .lm.fit(x_train_ar, y_train)

        # Predict & Combine
        pred                  <-  model_ar$coefficients %*% x_pred_ar[,]
        preds_ar2[t+1, "AR"]  <-  pred
        se_ar2[t+1, "AR"]     <-  (y_pred - pred) ** 2
    }

    ##### TV-C Models ##### 
    # Set Target Variable
    Y  <-  dataset[,  1, drop = FALSE]
    
    # Set 'Simple' Signals
    X  <-  dataset[, -1, drop = FALSE]

    # Load External Point Forecasts (Koop & Korobilis 2023)
    F  <-  get(paste0("Ext_PF_", target_var_names[p]))

    # Set TV-C-Parameter
    sample_length  <-  4 * 3
    lambda_grid    <-  c(0.90, 0.95, 0.99, 0.999, 1) 
    kappa_grid     <-  0.98
    n_cores        <-  1

    # Apply TV-C-Function
    results  <-  hdflex::tvc(Y, 
                             X,
                             F, 
                             lambda_grid,
                             kappa_grid,
                             sample_length,
                             n_cores)
                             
    # Assign Results
    forecast_tvc      <-  results[[1]]
    variance_tvc      <-  results[[2]]
    model_names_tvc   <-  colnames(forecast_tvc)
    
    # Define Cut Length and Trim Objects
    sample_period_idx  <-  80:full_length   
    sub_forecast_tvc   <-  forecast_tvc[sample_period_idx, , drop = FALSE]
    sub_variance_tvc   <-  variance_tvc[sample_period_idx, , drop = FALSE]
    sub_Y              <-  Y[sample_period_idx, , drop = FALSE]
    sub_dates          <-  full_dates[sample_period_idx]
    sub_length         <-  length(sub_dates)

    ##### Dynamic Subset Combination ##### 
    # Set DSC-Parameter
    nr_mods     <-  ncol(sub_forecast_tvc)
    gamma_grid  <-  c(0.4, 0.5, 0.6, 0.7, 0.8, 0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96, 0.97, 0.98, 0.99, 0.999, 1.00)
    psi_grid    <-  c(1:100)
    delta       <-  0.95
    n_cores     <-  1

    # Apply DSC-Function
    results  <-  hdflex::dsc(gamma_grid,
                             psi_grid,
                             sub_Y,
                             sub_forecast_tvc,
                             sub_variance_tvc,
                             delta,
                             n_cores)

    # Assign Results
    sub_forecast_stsc    <-  results[[1]]
    sub_variance_stsc    <-  results[[2]]
    sub_chosen_gamma     <-  results[[3]]
    sub_chosen_psi       <-  results[[4]]
    sub_pred_pockets     <-  results[[5]]

    # Define Evaluation Period 
    eval_date_start      <-  "1991-01-01" 
    eval_date_end        <-  "2021-12-31"     
    eval_period_idx      <-  which(sub_dates > eval_date_start & sub_dates <= eval_date_end)

    # Trim Objects
    oos_Y                <-  sub_Y[eval_period_idx, ]
    oos_benchmark        <-  preds_ar2[rownames(preds_ar2) > eval_date_start, "AR"] 
    oos_forecast_stsc    <-  sub_forecast_stsc[eval_period_idx]
    oos_variance_stsc    <-  sub_variance_stsc[eval_period_idx]
    oos_chosen_gamma     <-  sub_chosen_gamma[eval_period_idx]
    oos_chosen_psi       <-  sub_chosen_psi[eval_period_idx]
    oos_pred_pockets     <-  sub_pred_pockets[eval_period_idx, , drop = FALSE]
    oos_length           <-  length(eval_period_idx)
    oos_dates            <-  sub_dates[eval_period_idx]

    # Add Dates
    names(oos_forecast_stsc)   <-  oos_dates
    names(oos_variance_stsc)   <-  oos_dates
    names(oos_chosen_gamma)    <-  oos_dates
    names(oos_chosen_psi)      <-  oos_dates
    rownames(oos_pred_pockets) <-  oos_dates

    ##### Evaluate ##### 
    # Apply Statistial-Evaluation-Function
    summary_results  <-  summary_stsc(oos_Y,
                                      oos_benchmark,
                                      oos_forecast_stsc) 
     # Assign MSE-Results
    mse  <-  summary_results[[4]]

    # Return
    return(c(mse[[2]], mse[[1]]))

}))

# MSE-Results
dimnames(results)  <-  list(target_var_names, c("AR", "STSC"))
round(results / results[, 1], 4)
```


### Authors
Philipp Ad채mmer, Sven Lehmann and Rainer Sch체ssler

### License

MIT
